HO unification from object language to meta language

### 2024-04-02 paper/main.tex
impl of progress-beta consistent with tex

\begin{definition}[\progBetaLL]
  A link \linkbetaM{\Gamma}{X}{N_S\appsep [t|L]} is removed from \linkStore, if
  it exists a substitution $\gamma$, such that the first term $t$ is a name no
  occurring in $S$. In this case, let $M$ a fresh variable, then the new links
  \linkbetaM{\Gamma,x}{X}{M_{S,n}\appsep L} and \linketaM{\Gamma}{N}{\lambda
  x.M_x} are added to \linkStore.
\end{definition}

\begin{definition}[\progBetaRH]
  A link \linkbetaM{\Gamma}{X}{\rhsBeta} is removed from
  \linkStore if $N_S$ is instantiated to a term $t$ and the
  $\beta$-reduced term $t'$ obtained from the application of $t$ to
  $L$ is in \llambda. Moreover, $X$ is unified to $t$.
\end{definition}

@@

\begin{proof}[Proof sketch]
  TODO: bla
\end{proof}

\begin{corollary}
  Given \linkbetaM{\Gamma}{X}{\rhsBeta}, then \elpiIn{distinct-name} $S$ holds.  
\end{corollary}

>>>>

\begin{definition}[\progBetaLL]
  A link \linkbetaM{\Gamma}{X}{N_S\appsep [t|L]} is removed from \linkStore, if
  it exists a substitution $\gamma$, such that the first term $t$ is a name no
  occurring in $S$. In this case, let $M$ a fresh variable, then the new link
  \linkbetaM{\Gamma,x}{X}{M_{S,n}\appsep L} is added to \linkStore and if $L =
  []$, then $X$ is unified with $M_{S,n}$, otherwise, the
  \linketaM{\Gamma}{N}{\lambda x.M_x} is added to \linkStore.
  \label{def:progBetaLL}
\end{definition}

\begin{definition}[\progBetaRH]
  A link \linkbetaM{\Gamma}{X}{\rhsBeta} is removed from
  \linkStore if $N_S$ is instantiated to a term $t$ and the
  $\beta$-reduced term $t'$ obtained from the application of $t$ to
  $L$ is in \llambda. Moreover, $X$ is unified to $t$.
  \label{def:progBetaRH}
\end{definition}

@@

\begin{proof}[Proof sketch]
  By \cref{def:progBetaRH}, the \linkbeta is removed from \linkStore, hence 
  they cannot be applied indefinitely. If the \linkbeta is progressed due to
  \progBetaLL, then two links are added, the first 
\end{proof}

\begin{corollary}
  Given a \linkbeta, the scope of its \rhs variables in \llambda.
\end{corollary}

\begin{proof}[Proof sketch]
  By construction, the \rhs of \linkbeta is of the form \rhsBeta and $S$ is in
  \llambda. If a \linkbeta is triggered by \progBetaRH, then, by
  \cref{def:progBetaRH} that link is removed by \linkStore, and the property is
  satisfied. If the \linketa is activated by \progBetaLL, then, by
  \cref{def:progBetaLL}, $L = [n|L']$ and the scope `$S,x$', is in \llambda. 
\end{proof}
